Ordnung ist das halbe Leben -- Establishing Totally Ordered HTN Planning Problems is Half the Job (to Getting them Solved More Efficiently)

### 2022-11-26 paper/paper-mainfile.tex
semi-final draft?

\subsection{Complex Inference of Effects for Compound Tasks (for Grounded Domain) }
The work by~\cite{ConnyPreEstimation}, details a way to infer a subset of the mandatory preconditions and effects.

@@

There exists a polynomial-time algorithm for inferring the mandatory preconditions and precondition-relaxed effects, see \cite{ConnyPreEstimation} for details.
In this paper, we will be utilising both of these, as seen in the next section.
%the precondition-relaxed possible effects, which may hold after at least one refinement of c.

@@

We will now prove that our algorithm preserves at least one solution as long as Algorithm~\ref{alg:Algorithm1} uses simple inference or preconditions and possible effects from complex inference, and this criterion is met.

%\textit{Note that this criteria does not apply if using preconditions and guaranteed effects from complex inference}, as those are a \emph{subset} of possible preconditions and effects -- and thus there may be other, unknown effects that impact the executability of the sequence produced by Algorithm~\ref{alg:Algorithm1}.

%Specifically, unknown mandatory delete effects may render the chose linearization un-executable. Otherwise, it is notable that mandatory effects all occur in the state.

%On the other hand possible preconditions and effects - if they never occur, that's also a problem the PO version has to deal with.

@@

	The linearization of this method would have drawn an ordering $(t_i, t_k)$ due to the way the algorithm defines $prec^{*}, add^{*}$ etc. We are assuming that all methods meet the linearization criteria, so $(t_i, t_k)$ should not be required. This safely enforces $(a_k, a_0)$ ordering in the final TO plan, meaning $a_0$ is not the first action in the resulting total order imposed by the algorithm. In other words, if $a_k$’s precondition could be met by any action $a_i$, $a_i$ would be ordered in front of it.

@@

\subsection{Theoretical Properties If Using Complex Inference}
Unfortunately, no criteria for determining if a solution is guaranteed to exist when using the second inference method, since there may always be unknown preconditions and effects in the precondition-relaxed effects.

@@

\subsection{Hardware and Planning Systems}
The empirical evaluation was conducted on a machine with 30GiB of memory and 4 vCPUs, each with 2 GiB RAM. Recent work by \cite{HTN2SAS} shows that the PO panda$_\pi$, achieved similar coverage and slightly lower IPC score than all TO planners tested. %Lilotane by \cite{Lilotane} is an TOHTN solver and the IPC 2020 runner-up. The winner, HyperTensioN by \cite{hypertension} could not be tested due to lack of support for reading in optimisation metrics.

@@

Unfortunately, when using simple inference, there are very few problems for which all partially ordered methods are linearized without conflict.
Fortunately, when using complex inference, most partially ordered methods in all problems are linearized without conflict.
Figure~\ref{fig:ProblemsLinearizedWOCycleBreak} shows the comparison between the two.

@@

\begin{table*}
	\centering
	\caption{Coverage achieved, using Simple Inference on Lifted Problems}
	\label{table:LiftedSimpleCoverage}
	\scalebox{0.7} {
		\begin{tabular}{lccccccccccccccccccl} 
			\toprule 
			&& \multicolumn{2}{c}{rc2(Add)} & \multicolumn{2}{c}{rc2(Filter)} & \multicolumn{2}{c}{rc2(FF)} & \multicolumn{2}{c}{rc2(LMC)}  & \multicolumn{2}{c}{Lilotane}\\ 
			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10} \cmidrule(lr){11-12}  
			& max &PO & TO & PO & TO & PO & TO & PO &\multicolumn{2}{c}{ TO  } \\ 
			\midrule 
			Barman-BDI & 20 & 3.0 & \textbf{10.0} & 3.0 & \textbf{10.0} & 3.0 & \textbf{10.0} & 2.0 & \textbf{9.0} &\multicolumn{2}{c}{ \textbf{17.0}  } \\ 
			Monroe Fully Observ.$^{7,7,7,5,0}$ & 25 & \textbf{25.0} & \textbf{25.0} & 18.0 & \textbf{22.0} & 22.0 & \textbf{23.0} & \textbf{15.0} & \textbf{15.0} &\multicolumn{2}{c}{ 18.0  } \\ 
			Monroe Part. Observ.$^{2,2,2,2,0}$ & 24 & \textbf{14.0} & 13.0 & \textbf{7.0} & 6.0 & \textbf{14.0} & 13.0 & \textbf{11.0} & 9.0 &\multicolumn{2}{c}{ \textbf{20.0}  } \\ 
			PCP$^{18,18,17,17}$ & 18 & \textbf{15.0} & \textbf{15.0} & \textbf{15.0} & \textbf{15.0} & \textbf{14.0} & \textbf{14.0} & \textbf{14.0} & \textbf{14.0} &\multicolumn{2}{c}{ 0.0  } \\ 
			Rover & 20 & 6.0 & \textbf{15.0} & 4.0 & \textbf{13.0} & 4.0 & \textbf{14.0} & 4.0 & \textbf{13.0} &\multicolumn{2}{c}{ \textbf{20.0}  } \\ 
			Satellite & 25 & 24.0 & \textbf{25.0} & 22.0 & \textbf{25.0} & \textbf{25.0} & \textbf{25.0} & 24.0 & \textbf{25.0} &\multicolumn{2}{c}{ \textbf{25.0}  } \\ 
			Transport & 40 & 12.0 & \textbf{27.0} & \textbf{2.0} & \textbf{2.0} & 13.0 & \textbf{14.0} & 7.0 & \textbf{12.0} &\multicolumn{2}{c}{ \textbf{35.0}  } \\ 
			UM-Translog$^{1,1,1,1,0}$ & 22 & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} &\multicolumn{2}{c}{ 21.0  } \\ 
			Woodworking & 30 & \textbf{13.0} & 7.0 & \textbf{8.0} & 7.0 & \textbf{12.0} & 7.0 & \textbf{9.0} & 7.0 &\multicolumn{2}{c}{ 6.0  } \\ 
			\midrule 
			Monroe & 100 & \textbf{96.0} & 92.0 & 79.0 & \textbf{87.0} & \textbf{92.0} & 90.0 & 81.0 & \textbf{89.0} &\multicolumn{2}{c}{ \textbf{100.0}  } \\ 
			SmartPhone$^{3,3,3,3,0}$ & 7 & 5.0 & \textbf{7.0} & 5.0 & \textbf{6.0} & 5.0 & \textbf{6.0} & 5.0 & \textbf{6.0} &\multicolumn{2}{c}{ 1.0  } \\ 
			Zenotravel & 5 & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} &\multicolumn{2}{c}{ \textbf{5.0}  } \\ 
			\midrule 
			Coverage & 336 & 240.0 & \textbf{263.0} & 190.0 & \textbf{220.0} & 231.0 & \textbf{243.0} & 199.0 & \textbf{226.0} &\multicolumn{2}{c}{ \textbf{268.0}  } \\ 
			Norm. coverage & 12 & 8.23 & \textbf{9.45} & 6.9 & \textbf{8.12} & 8.0 & \textbf{8.83} & 7.14 & \textbf{8.18} &\multicolumn{2}{c}{ 8.58  } \\ 
			\bottomrule 
		\end{tabular} 
	}
\end{table*}

\begin{table*}
	\centering
	\caption{IPC score achieved, using Simple Inference on Lifted Problems}
	\label{table:LiftedSimpleIPC}
	\scalebox{0.7} {
		\begin{tabular}{lccccccccccccccccccl} 
			\toprule 
			&& \multicolumn{2}{c}{rc2(Add)} & \multicolumn{2}{c}{rc2(Filter)} & \multicolumn{2}{c}{rc2(FF)} & \multicolumn{2}{c}{rc2(LMC)}  & \multicolumn{2}{c}{Lilotane} \\ 
			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10} \cmidrule(lr){11-12}  
			& max &PO & TO & PO & TO & PO & TO & PO &\multicolumn{2}{c}{ TO  } \\ 
			\midrule 
			Barman-BDI & 1 & 0.07 & \textbf{0.38} & 0.07 & \textbf{0.34} & 0.07 & \textbf{0.35} & 0.05 & \textbf{0.23} &\multicolumn{2}{c}{ \textbf{0.72}  } \\ 
			Monroe Fully Observ.$^{7,7,7,5,0}$ & 1 & \textbf{0.56} & 0.52 & 0.32 & \textbf{0.33} & \textbf{0.47} & 0.45 & \textbf{0.22} & 0.21 &\multicolumn{2}{c}{ 0.54  } \\ 
			Monroe Part. Observ.$^{2,2,2,2,0}$ & 1 & \textbf{0.31} & 0.28 & \textbf{0.14} & 0.13 & \textbf{0.31} & 0.29 & \textbf{0.17} & 0.16 &\multicolumn{2}{c}{ \textbf{0.63}  } \\ 
			PCP$^{18,18,17,17}$ & 1 & \textbf{0.83} & \textbf{0.83} & \textbf{0.83} & \textbf{0.83} & \textbf{0.82} & \textbf{0.82} & \textbf{0.82} & \textbf{0.82} &\multicolumn{2}{c}{ 0.0  } \\ 
			Rover & 1 & 0.28 & \textbf{0.61} & 0.14 & \textbf{0.49} & 0.2 & \textbf{0.56} & 0.17 & \textbf{0.42} &\multicolumn{2}{c}{ \textbf{0.97}  } \\ 
			Satellite & 1 & 0.9 & \textbf{1.0} & 0.76 & \textbf{1.0} & 0.99 & \textbf{1.0} & 0.89 & \textbf{0.99} &\multicolumn{2}{c}{ \textbf{1.0}  } \\ 
			Transport & 1 & 0.24 & \textbf{0.6} & 0.04 & \textbf{0.05} & 0.27 & \textbf{0.32} & 0.12 & \textbf{0.2} &\multicolumn{2}{c}{ \textbf{0.78}  } \\ 
			UM-Translog$^{1,1,1,1,0}$ & 1 & \textbf{1.0} & 0.99 & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} &\multicolumn{2}{c}{ 0.92  } \\ 
			Woodworking & 1 & \textbf{0.38} & 0.23 & 0.2 & \textbf{0.23} & \textbf{0.36} & 0.23 & \textbf{0.27} & 0.23 &\multicolumn{2}{c}{ 0.2  } \\ 
			\midrule 
			Monroe & 1 & \textbf{0.77} & 0.74 & \textbf{0.5} & 0.47 & \textbf{0.76} & 0.73 & \textbf{0.54} & 0.51 &\multicolumn{2}{c}{ \textbf{0.96}  } \\ 
			SmartPhone$^{3,3,3,3,0}$ & 1 & 0.71 & \textbf{1.0} & 0.69 & \textbf{0.85} & 0.71 & \textbf{0.86} & 0.71 & \textbf{0.83} &\multicolumn{2}{c}{ 0.14  } \\  
			Zenotravel & 1 & \textbf{1.0} & \textbf{1.0} & 0.64 & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & 0.83 & \textbf{1.0} &\multicolumn{2}{c}{ \textbf{1.0}  } \\ 
			\midrule 
			IPC score & 12 & 7.1 & \textbf{8.2} & 5.3 & \textbf{6.7} & 7.0 & \textbf{7.6} & 5.8 & \textbf{6.6} &\multicolumn{2}{c}{ 7.9  } \\ 
			\bottomrule 
		\end{tabular} 
	}
\end{table*}

\begin{table*}
	\centering
	\caption{Coverage achieved, using Complex Inference}
	\label{table:GroundedComplexCoverage}.
	\scalebox{0.8} {
		\begin{tabular}{lccccccccccccccccl} 
			\toprule 
		\end{tabular}  
	}
\end{table*}

\begin{table*}
	\centering
	\caption{IPC score achieved, using Complex Inference}
	\label{table:GroundedComplexIPC}.
	\scalebox{0.9} {
		\begin{tabular}{lccccccccccccccccl} 
			\toprule 
		\end{tabular}
	}
\end{table*}

\begin{figure*}
	\caption{Percentage of Problems Linearized Without Cycle-break for each Domain and each Inference Method}
	\label{fig:ProblemsLinearizedWOCycleBreak}
	\centering
	\includegraphics[width=14cm]{figures/Lin_criteria_C_vs_S.jpg}
\end{figure*}

>>>>

\subsection{Complex Inference of Preconditions and Effects for Compound Tasks (for Grounded Domain) }
The work by~\cite{ConnyPreEstimation}, details a way to infer executability-relaxed preconditions and effects. Specifically, for a compound task $c$, they are a subset of the mentioned literals described in the Simple Inference section, and a super-set of the actual preconditions and effects for any given refinement and execution of a task $c$.

@@

A fact $f \in F$ is an \emph{executability-relaxed precondition} of $c$ if and only if for all t.o. refinements (ignoring executability of the refinement) $\langle a_0 ... a_n \rangle$ of $c$ there exists an action $a_i$ with $f \in \prec(a_i)$ and there does not exist an action $a_j$ with $j < i$ and $f \in add(a_j)$, where $i, j \in \{0, ..., n\}$.

There exists a polynomial-time algorithm for inferring the executability-relaxed preconditions and precondition-relaxed effects, see \cite{ConnyPreEstimation} for details.
In this paper, we will be utilising both of these, as seen in the next section.
%the precondition-relaxed possible effects, which may hold after at least one refinement of c.

@@

%IT ONLY WORKS IF *ALL* METHODS CAN BE CYCLE-BREAKED.

\begin{theorem} \label{thm:RelaxedPreconditions}
	Given a POHTN planning problem $P$ and TOHTN problem $P'$ obtained from $P$ by using Algorithm~\ref{alg:Algorithm1}, \emph{only if $P$, the entire problem meets the linearization criteria},
	then we know executability-relaxed preconditions for any $c$ are indeed the only ones needed to execute any refinement of $c$.
\end{theorem}
\begin{proof}
	At least in our special case, we can be assured that the executability-relaxed preconditions actually work for us.

	For some method with at least two sub-tasks, $a$ and $b$,
	the desired orderings are to put $a$ with $f \in \Add(a)$ before $a_i$ with $f \in \Pre(a_i)$. We're assuming no cycle-breaking, so this was actually achieved. If such a precondition can't be met this way, (such an $a_j$ does not exist, or the method already enforces that $b$ executes after $a_i$) by definition it must be in the executability-relaxed preconditions calculated.

	Therefore, any precondition of $c$'s children that can't be met by other placing $c$'s children before it is part - \emph{so it is indeed a super-set of actual preconditions}(assuming no cycle-breaking was needed).

	If even one partially ordered method did need cycle-breaking, than of course it means nothing - we may indeed need other preconditions to make refinements of $c$ executable. Then those results no longer hold.
\end{proof}

We use Theorem~\ref{thm:RelaxedPreconditions} as support for the following main result. We will now prove that our algorithm preserves at least one solution as long as Algorithm~\ref{alg:Algorithm1} uses simple inference or preconditions and possible effects from complex inference, and this criterion is met.

@@

	The linearization of this method would have drawn an ordering $(t_i, t_k)$ due to the way the algorithm defines $prec^{*}, add^{*}$ etc. We are assuming that all methods meet the linearization criteria, so $(t_i, t_k)$ should not be required, either directly or via inheritance from parent tasks. This safely enforces $(a_k, a_0)$ ordering in the final TO plan, meaning $a_0$ is not the first action in the resulting total order imposed by the algorithm. In other words, if $a_k$’s precondition could be met by any action $a_i$, $a_i$ would be ordered in front of it.

@@

@@

\subsection{Hardware and Planning Systems}
The empirical evaluation was conducted on a machine with 30GiB of memory and 4 vCPUs, each with 2 GiB RAM. Recent work by \cite{HTN2SAS} shows that the PO panda$_\pi$, achieved similar coverage and slightly lower IPC score than the best TO planner tested. Also tested is HyperTensioN by \cite{hypertension} an TOHTN solver and the IPC 2020 winner, and Lilotane by \cite{Lilotane} another TOHTN solver and the IPC 2020 runner-up.

@@

Unfortunately, when using simple inference, there are very few problems for which all partially ordered methods are linearized without conflict.
Fortunately, when using complex inference, most partially ordered methods in all problems are linearized without conflict.
Figure~\ref{ffig:MethodsLinearizedWOCycleBreak} shows the comparison between the two.

@@

\begin{table*}
	\centering
	\caption{Coverage achieved, using Simple Inference on Lifted Problems}
	\label{table:LiftedSimpleCoverage}
	\scalebox{0.6} {
		\begin{tabular}{lccccccccccccccccccl} 
			\toprule 
			&& \multicolumn{2}{c}{rc2(Add)} & \multicolumn{2}{c}{rc2(Filter)} & \multicolumn{2}{c}{rc2(FF)} & \multicolumn{2}{c}{rc2(LMC)}  & \multicolumn{2}{c}{Lilotane} & \multicolumn{2}{c}{HyperTensioN} \\  
			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10} \cmidrule(lr){11-12}   \cmidrule(lr){13-14} 
			& max &PO & TO & PO & TO & PO & TO & PO &  TO  \\ 
			\midrule 
			Barman-BDI & 20 & 3.0 & \textbf{10.0} & 3.0 & \textbf{10.0} & 3.0 & \textbf{10.0} & 2.0 & \textbf{9.0} &\multicolumn{2}{c}{ \textbf{17.0}  } \\ 
			Monroe Fully Observ.$^{7,7,7,5,0}$ & 25 & \textbf{25.0} & \textbf{25.0} & 18.0 & \textbf{22.0} & 22.0 & \textbf{23.0} & \textbf{15.0} & \textbf{15.0} &\multicolumn{2}{c}{ 18.0  } \\ 
			Monroe Part. Observ.$^{2,2,2,2,0}$ & 24 & \textbf{14.0} & 13.0 & \textbf{7.0} & 6.0 & \textbf{14.0} & 13.0 & \textbf{11.0} & 9.0 &\multicolumn{2}{c}{ \textbf{20.0}  } \\ 
			PCP$^{18,18,17,17}$ & 18 & \textbf{15.0} & \textbf{15.0} & \textbf{15.0} & \textbf{15.0} & \textbf{14.0} & \textbf{14.0} & \textbf{14.0} & \textbf{14.0} &\multicolumn{2}{c}{ 0.0  } \\ 
			Rover & 20 & 6.0 & \textbf{15.0} & 4.0 & \textbf{13.0} & 4.0 & \textbf{14.0} & 4.0 & \textbf{13.0} &\multicolumn{2}{c}{ \textbf{20.0}  } \\ 
			Satellite & 25 & 24.0 & \textbf{25.0} & 22.0 & \textbf{25.0} & \textbf{25.0} & \textbf{25.0} & 24.0 & \textbf{25.0} &\multicolumn{2}{c}{ \textbf{25.0}  } \\ 
			Transport & 40 & 12.0 & \textbf{27.0} & \textbf{2.0} & \textbf{2.0} & 13.0 & \textbf{14.0} & 7.0 & \textbf{12.0} &\multicolumn{2}{c}{ \textbf{35.0}  } \\ 
			UM-Translog$^{1,1,1,1,0}$ & 22 & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} &\multicolumn{2}{c}{ 21.0  } \\ 
			Woodworking & 30 & \textbf{13.0} & 7.0 & \textbf{8.0} & 7.0 & \textbf{12.0} & 7.0 & \textbf{9.0} & 7.0 &\multicolumn{2}{c}{ 6.0  } \\ 
			\midrule 
			Monroe & 100 & \textbf{96.0} & 92.0 & 79.0 & \textbf{87.0} & \textbf{92.0} & 90.0 & 81.0 & \textbf{89.0} &\multicolumn{2}{c}{ \textbf{100.0}  } \\ 
			SmartPhone$^{3,3,3,3,0}$ & 7 & 5.0 & \textbf{7.0} & 5.0 & \textbf{6.0} & 5.0 & \textbf{6.0} & 5.0 & \textbf{6.0} &\multicolumn{2}{c}{ 1.0  } \\ 
			Zenotravel & 5 & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} &\multicolumn{2}{c}{ \textbf{5.0}  } \\ 
			\midrule 
			Coverage & 336 & 240.0 & \textbf{263.0} & 190.0 & \textbf{220.0} & 231.0 & \textbf{243.0} & 199.0 & \textbf{226.0} &\multicolumn{2}{c}{ \textbf{268.0}  } \\ 
			Norm. coverage & 12 & 8.23 & \textbf{9.45} & 6.9 & \textbf{8.12} & 8.0 & \textbf{8.83} & 7.14 & \textbf{8.18} &\multicolumn{2}{c}{ 8.58  } \\ 
			\bottomrule 
		\end{tabular} 
	}
\end{table*}

\begin{table*}
	\centering
	\caption{IPC score achieved, using Simple Inference on Lifted Problems}
	\label{table:LiftedSimpleIPC}
	\scalebox{0.6} {
		\begin{tabular}{lccccccccccccccccccl} 
			\toprule 
			&& \multicolumn{2}{c}{rc2(Add)} & \multicolumn{2}{c}{rc2(Filter)} & \multicolumn{2}{c}{rc2(FF)} & \multicolumn{2}{c}{rc2(LMC)}  & \multicolumn{2}{c}{Lilotane} & \multicolumn{2}{c}{HyperTensioN} \\ 
			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10} \cmidrule(lr){11-12}   \cmidrule(lr){13-14} 
			& max &PO & TO & PO & TO & PO & TO & PO & TO   \\ 
			\midrule 
			Barman-BDI & 1 & 0.07 & \textbf{0.38} & 0.07 & \textbf{0.34} & 0.07 & \textbf{0.35} & 0.05 & \textbf{0.23} &\multicolumn{2}{c}{ \textbf{0.72}  } \\ 
			Monroe Fully Observ.$^{7,7,7,5,0}$ & 1 & \textbf{0.56} & 0.52 & 0.32 & \textbf{0.33} & \textbf{0.47} & 0.45 & \textbf{0.22} & 0.21 &\multicolumn{2}{c}{ 0.54  } \\ 
			Monroe Part. Observ.$^{2,2,2,2,0}$ & 1 & \textbf{0.31} & 0.28 & \textbf{0.14} & 0.13 & \textbf{0.31} & 0.29 & \textbf{0.17} & 0.16 &\multicolumn{2}{c}{ \textbf{0.63}  } \\ 
			PCP$^{18,18,17,17}$ & 1 & \textbf{0.83} & \textbf{0.83} & \textbf{0.83} & \textbf{0.83} & \textbf{0.82} & \textbf{0.82} & \textbf{0.82} & \textbf{0.82} &\multicolumn{2}{c}{ 0.0  } \\ 
			Rover & 1 & 0.28 & \textbf{0.61} & 0.14 & \textbf{0.49} & 0.2 & \textbf{0.56} & 0.17 & \textbf{0.42} &\multicolumn{2}{c}{ \textbf{0.97}  } \\ 
			Satellite & 1 & 0.9 & \textbf{1.0} & 0.76 & \textbf{1.0} & 0.99 & \textbf{1.0} & 0.89 & \textbf{0.99} &\multicolumn{2}{c}{ \textbf{1.0}  } \\ 
			Transport & 1 & 0.24 & \textbf{0.6} & 0.04 & \textbf{0.05} & 0.27 & \textbf{0.32} & 0.12 & \textbf{0.2} &\multicolumn{2}{c}{ \textbf{0.78}  } \\ 
			UM-Translog$^{1,1,1,1,0}$ & 1 & \textbf{1.0} & 0.99 & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} &\multicolumn{2}{c}{ 0.92  } \\ 
			Woodworking & 1 & \textbf{0.38} & 0.23 & 0.2 & \textbf{0.23} & \textbf{0.36} & 0.23 & \textbf{0.27} & 0.23 &\multicolumn{2}{c}{ 0.2  } \\ 
			\midrule 
			Monroe & 1 & \textbf{0.77} & 0.74 & \textbf{0.5} & 0.47 & \textbf{0.76} & 0.73 & \textbf{0.54} & 0.51 &\multicolumn{2}{c}{ \textbf{0.96}  } \\ 
			SmartPhone$^{3,3,3,3,0}$ & 1 & 0.71 & \textbf{1.0} & 0.69 & \textbf{0.85} & 0.71 & \textbf{0.86} & 0.71 & \textbf{0.83} &\multicolumn{2}{c}{ 0.14  } \\  
			Zenotravel & 1 & \textbf{1.0} & \textbf{1.0} & 0.64 & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & 0.83 & \textbf{1.0} &\multicolumn{2}{c}{ \textbf{1.0}  } \\ 
			\midrule 
			IPC score & 12 & 7.1 & \textbf{8.2} & 5.3 & \textbf{6.7} & 7.0 & \textbf{7.6} & 5.8 & \textbf{6.6} &\multicolumn{2}{c}{ 7.9  } \\ 
			\bottomrule 
		\end{tabular} 
	}
\end{table*}

\begin{table*}
	\centering
	\caption{Coverage achieved, using Complex Inference}
	\label{table:GroundedComplexCoverage}.
	\scalebox{0.8} {
		\begin{tabular}{lccccccccccccccccl} 
			\toprule 
			&& \multicolumn{2}{c}{rc2(Add)} & \multicolumn{2}{c}{rc2(Filter)} & \multicolumn{2}{c}{rc2(FF)} & \multicolumn{2}{c}{rc2(LMC)} & \multicolumn{2}{c}{HyperTensioN} & \multicolumn{2}{c}{Lilotane} \\ 
			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10}     \cmidrule(lr){11-12} \cmidrule(lr){13-14}  
			& max &PO & TO & PO & TO & PO & TO & PO & TO \\ 
			\midrule 
			Barman-BDI  \\ 
			Monroe Fully Observ.$^{2}$   \\ 
			Monroe Part. Observ.$^{2}$  \\ 
			PCP$^{17}$  \\ 
			Rover  \\ 
			Satellite   \\  
			Transport   \\ 
			UM-Translog$^{1}$  \\ 
			Woodworking$^{2}$  \\ 
			\midrule 
			Monroe   \\ 
			SmartPhone$^{1}$   \\ 
			Zenotravel   \\ 
			\midrule 
			Coverage  \\ 
			Norm. coverage  \\ 
			\bottomrule 
		\end{tabular}  
	}
\end{table*}

\begin{table*}
	\centering
	\caption{IPC score achieved, using Complex Inference}
	\label{table:GroundedComplexIPC}.
	\scalebox{0.8} {
		\begin{tabular}{lccccccccccccccccl} 
			\toprule 
&& \multicolumn{2}{c}{rc2(Add)} & \multicolumn{2}{c}{rc2(Filter)} & \multicolumn{2}{c}{rc2(FF)} & \multicolumn{2}{c}{rc2(LMC)} & \multicolumn{2}{c}{HyperTensioN} & \multicolumn{2}{c}{Lilotane} \\ 
\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10}   \cmidrule(lr){11-12} \cmidrule(lr){13-14}  
& max &PO & TO & PO & TO & PO & TO & PO & TO \\ 
\midrule 
Barman-BDI  \\ 
Monroe Fully Observ.$^{2}$   \\ 
Monroe Part. Observ.$^{2}$  \\ 
PCP$^{17}$  \\ 
Rover  \\ 
Satellite   \\  
Transport   \\ 
UM-Translog$^{1}$  \\ 
Woodworking$^{2}$  \\ 
\midrule 
Monroe   \\ 
SmartPhone$^{1}$   \\ 
Zenotravel   \\ 
\midrule 
IPC score \\
\bottomrule 
\end{tabular}  
	}
\end{table*}

%\begin{figure*}
%	\caption{Percentage of Problems Linearized Without Cycle-break for each Domain and each Inference Method}
%	\label{fig:ProblemsLinearizedWOCycleBreak}
%	\centering
%	\includegraphics[width=14cm]{figures/Lin_criteria_C_vs_S.jpg}
%\end{figure*}

\begin{figure*}
	\caption{For Grounded Problems, Average Percentage of Methods Linearized Without Cycle-break for Each Domain and for Each Inference Method}
	\label{fig:MethodsLinearizedWOCycleBreak}
	\centering
	\includegraphics[width=14cm]{figures/Lin_average_C_vs_S.jpg}
\end{figure*}
